---
title: "Redesigns (2/2)"
editor: visual
---

```{r}
library(plotly)
data <- data.frame(
  month = factor(c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec", "Jan", "Feb", "Mar", "Apr"),
                 levels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec")),
  collapses = c(7, 6, 16, 17, 20, 28, 46, 57, 81, 109, 116, 124, 126, 73, 120, 55),
  deaths = c(4, 4, 8, 10, 7, 19, 33, 34, 43, 64, 77, 90, 86, 51, 83, 36)
)

# Create a plotly line plot
plot_ly(data, x = ~month, y = ~collapses, type = 'scatter', mode = 'lines', name = 'Collapses') %>%
  add_trace(y = ~deaths, name = 'Deaths') %>%
  layout(title = "Athlete Collapses and Deaths",
         xaxis = list(title = "Month"),
         yaxis = list(title = "Count", tickvals = c(0, 10, 20, 30,40,50,60,70,80,90,100,120)))
```

We can clearly see the trend over time in this line chart. We can see that collapses are much more than deaths. The graph also shows reasonable values on y-axis. However, inorder to clearly distinguish the collapses and deaths per month, we can redesign into below graph for clear visuals.

```{r}

library(plotly)

data <- data.frame(
  month = factor(c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec", 
                   "Jan", "Feb", "Mar", "Apr"), 
                 levels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec")),
  collapses = c(7, 6, 16, 17, 20, 28, 46, 57, 81, 109, 116, 124, 126, 73, 120, 55),
  deaths = c(4, 4, 8, 10, 7, 19, 33, 34, 43, 64, 77, 90, 86, 51, 83, 36)
)

# Create a Plotly column bar chart
plot_ly(data, x = ~month, y = ~collapses, type = 'bar', name = 'Collapses', marker = list(color = 'skyblue', line = list(color = 'darkblue', width = 1))) %>%
  add_trace(x = ~month, y = ~deaths, name = 'Deaths', marker = list(color = 'coral', line = list(color = 'darkred', width = 1))) %>%
  layout(title = "Athlete Collapses and Deaths",
         xaxis = list(title = "Month"),
         yaxis = list(title = "Frequencies", tickvals = c(0, 10, 20, 30,40,50,60,70,80,90,100,120)), barmode = 'group')
```

This code creates a separate bar chart for collapses and deaths, positioned side-by-side. This allows for easier visual comparison between the two variables.

By converting into bar graph:

-   One can easily visualize the data as graph is in 2D shape.

-   We can easily know the highest and lowest values in each month comparatively side by side.

-   We can interpret that there are more collapses than deaths in each month.
